\documentclass{article}
\usepackage{graphicx}
\usepackage{fancyhdr}

\pagestyle{fancy}
\lhead{EE568}
\rhead{Project Proposal}

\title{Pathfinder Role Playing Game\texttrademark Random Encounter Generator}
\author{Padraic Cashin, David Yambay, and Hai Zhuh}
\date{March 9, 2015}

\begin{document}
	\maketitle
	\newpage

	Pathfinder is a table-top role playing game developed by Paizo, similar to 
	Dungeons and Dragons.  Managing random monster encounters is one of the most time
	consuming, and difficult aspect of running the game, especially if the game master
	wants to maintain a certain level of variety among the encounters.  

	A good encounter should have the correct difficulty for the party, should contain 
	monsters that are reasonable based on the current terrain, for example the generator
	should never return polar bears if the players are currently in a arid desert, and 
	should contain a good mix of different monsters across many encounters.  The game 
	allows for this variety by allowing the game master to mix different monsters to 
	generate an encounter up to a difficulty threshold, as well as add templates to any
	of the monster, which change the effective level of the monster and augment its default
	abilities.  Some monsters can also have class levels, similar to the players, which
	could be added if time allows.

	Our initial implementation should include an graphical interface that will handle the 
	query creation and displaying of the encounter.  The database should contain a table 
	of monsters, a table of templates, and a table of traits common to all monsters.  
	Since monsters share many of same properties, those values could be moved into 
	other tables or relations if it makes sense to do so.  For the initial database, 
	it will contain the three tables, and a series of functions that will help us build 
	a valid encounter.  The only input from the user should be encounter level, 
	terrain type, preferred monster type and preferred templates. 

	In order to create the database, we plan on using a web scraper to grab infomation
	from the Pathfinder SRD.  This will allow us to populate the database quickly 
	so we can focus on developing and testing the encounter generating functions of the data
	base.  

	Pathfinder Role Playing Game\texttrademark is released under the Open Gaming Licence (OGL). 
\end{document}
